Higher Airy

### 2023-11-01 Higher_Airy.tex

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{eqnarray}
\usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
\usepackage{bm} %% for putting series names in bold
%%\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{xparse}
\usepackage{enumitem}
%\usepackage{eqnarray}
%% colors
\usepackage[svgnames]{xcolor}
\let\Re\relax
\DeclareMathOperator{\Re}{Re}
\let\Im\relax
\DeclareMathOperator{\Im}{Im}

%% editing
\newcommand{\done}[1]{\textcolor{gray}{#1}}

\theoremstyle{definition}
\newtheorem{defn}{Definition}
%%\theoremstyle{plain}
%%\newtheorem{prop}{Proposition}

% convenience aliases
\newcommand{\maps}{\colon}
\newcommand{\acts}{\mathbin{\raisebox{\depth}{\rotatebox{-90}{$\circlearrowright$}}}}

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{rotating}
\newcommand*{\isoarrow}[1]{\arrow[#1,"\rotatebox{90}{\(\sim\)}"
]}

@@

\newtheorem{definition}{Definition}[section]
\newtheorem{prop}[definition]{Proposition}
\newtheorem{remark}[definition]{Remark}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[definition]{Lemma}
%\newtheorem{conjecture}[definition]{Conjecture}
\newtheorem{claim}[definition]{Claim}
%\newtheorem{exercise}[definition]{Exercise}
\newtheorem*{notation*}{Notation}

\title{Borel regularity for ODEs and thimble integrals \\ \textbf{[DRAFT]}}
\author{Veronica Fantini and Aaron Fenyes}

@@

\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -\tfrac{1}{12}$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution \textcolor{magenta}{[check]}
\begin{equation}
e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples. As another example, you might rewrite the integral
\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
as
% see expansion.sage
\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. \textcolor{orange}{[Nikita has a complementary picture where the position domain is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. \textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$.

The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function \textcolor{orange}{that vanishes at $\infty$ [if it vanishes at $\infty$ it sent to zero, so why this assumption?]} to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ (see \cite[Theorem~C.11]{nikolaev2023existence}).
\end{defn}
\begin{defn}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{defn}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

\begin{enumerate}[start=4]
\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$. It turns out that $\hat{\Phi}$ is not only asymptotic to $\series{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
\end{enumerate}

The Borel summation process is summarized in the following diagram:
\begin{center}
\begin{tikzcd}
& \text{problem} & \\
\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
& & \\
\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi} \arrow[ll, mapsto, "\text{sum}"] 
\end{tikzcd}
\end{center}

You can't be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution. After all, $\series{\Phi}$ is asymptotic to lots of functions; Borel summation just picks one of them. In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem. The question of how that happens is the starting point for this paper.

%\color{gray}
%\begin{itemize}
%\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots}
%\begin{itemize}
%\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
%\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
%\item Feynman diagram series?
%\end{itemize}
%\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
%\begin{itemize}
%\item \done{Borel summation work in three steps. First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
%\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$. By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
%\item {[Draw the square!]}
%\end{itemize}
%\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
%\item In many cases, it picks correctly, producing an actual solution to your problem.
%\begin{itemize}
%\item The question of how that happens is the starting point for this paper.
%\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$. For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
%\end{itemize}
%\end{itemize}
%\color{black}
\subsection{A new perspective: Borel regularity}
\subsubsection{Introducing Borel regularity}
\begin{itemize}
\item Start instead with a holomorphic solution $\Phi$.
\item Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
\end{itemize}
%\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}

\begin{center}
\begin{tikzcd}
& \text{problem} & \\
\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
& & \\
\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
\end{tikzcd}
\end{center}
If $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
Since different functions can be asymptotic to the same power series, taking the Borel sum of the asymptotic series of $\Phi$ must smooth away some details. We'll therefore call this process {\em Borel regularization}. Explicitly, Borel regularization works in four steps.
\begin{enumerate}
\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
\item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before. This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.
\item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$. This is possible, by definition, if $\series{\Phi}$ is Borel-summable. \textbf{[Should we be allowed to take the Laplace transform at another points $b \in B$ instead?]}
\end{enumerate}
We'll say a function is {\em Borel-regularizable} if its asymptotic expansion is Borel-summable, ensuring that we can carry out the last two steps.

Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization. We'll say a function is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged. In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
\subsubsection{Borel regularity as a good approximation condition}
Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials. Watson showed a century ago \cite{watson} that a function $F$ that vanishes at $\infty$ is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around $\infty$ (see Definition~\ref{def:unif-gevrey-asymp}).

Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite{nikolaev2023exact} Theorem~B.15 and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}. These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north east] at (\size, \size) {$z$};
\end{tikzpicture}
\end{center}
When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north east] at (\size, \size) {$z$};
\end{tikzpicture}
\end{center}

%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular. Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity. Hence $\Phi$ is Borel-regularizable. In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$. In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity. 
\subsubsection{Borel regularity sometimes explains why Borel summation works}\label{borel-reg:explanatory-power}
The idea of Borel regularity can help us understand why Borel summation is so effective in some situations. Roughly speaking, Borel summation works well for problems with Borel regular solutions that stand out asymptotically \textcolor{magenta}{[this may need refining]}.

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[\S 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are entire functions of exponential type (i.e. $|R_j(z)|<C_j e^{a_j|z|}$ as $|z|\to+\infty$, for $C_j,a_j>0$ ).

We'll restrict our attention to the case where the roots of $P$ are distinct.

The form of $\mathcal{P}$ derives from Equation~2.2.3 \textcolor{orange}{(p.~105)} of \cite{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation still works well for the nonlinear ones, raising the question of whether our analysis generalizes.

\item the second problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}

\begin{equation}
I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
\end{equation}
where $f\colon X\to \mathbb{C}$ is a Morse function, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.  
\end{enumerate}

These two problems are closely linked. By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.

%Notice that our starting point is quite different: we assume $\Phi$ is a holomorphic functions such that it is either a thimble integral or it solves an ODE with irregular singularity at $\infty$. Then we prove $\Phi$ is Borel regular and in both cases, our proves follow the heuristic of the diagram above. We will give precise statements in the following section.

%%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
%%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray. We'll call it {\em Borel regularization}.
%%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information. We'll call this process {\em Borel regularization}.
%\begin{itemize}
%\item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
%\item We'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
%\item We have the following vector space inclusions:
%\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
%\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
%over all orders $N$ and all $z$ in a wide enough wedge around infinity. 
%
%Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
%\begin{itemize}
%\item $\Phi$ is Borel regular.
%\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
%\item $\phi$ grows at most exponentially along the Laplace transform ray.
%\end{itemize}
%\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible. \textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion. Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\tilde{\Phi}$ (i.e. it is Borel regular)? P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\tilde{\Phi}$, then $\tilde{\Phi}$ is of Gevrey type. In addition, every Gevrey type series $\tilde{\Phi}$ is the Gevrey asymptotics of a holomorphic function. When it is defined, the Borel sum of $\tilde{\Phi}$ is the natural holomorphic function asymptotic to $\tilde{\Phi}$.]}
%\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
%\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
%\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
%\item \ldots
%\end{itemize}

\subsection{Goals and Results}

First of all we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series. Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1}), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 3 of Theorem~\ref{thm:maxim}).

Second of all, we want to explain why it is useful to work in the Borel plane (the spatial domain): on the one hand integral equations are more regular than differential equations. On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.

\subsubsection{Why does Borel summation work for solutions of single level-$1$ ODEs?}
As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear single level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{A function $f$ is of exponential type if $|f(z)|\leq C e^{-a|z|}$ for $C,a>0$. Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}. Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully! It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.

\color{DarkTurquoise}
In \cite[Proposition~2.2.7]{EcalleIII}, where
\begin{align*}
P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
\end{align*}
(with the coefficients renamed to avoid a conflict with the zeros $\alpha_j$), the recurrence that gives the solution simplifies
\begin{align*} b_q & = P_q + Q_q z^{-1} - \frac{\partial}{\partial x^{(q)}} b(z, x, x^{(1)}, \ldots x^{(d)}) \\
& = P_q + Q_q z^{-1} - R_q(z^{-1}).
\end{align*}

Following the argument of Delabaere Lemma~6.2, we can prove that $\series{F}_j(z)$ is $1$-Gevrey by taking the formal Borel transform of the ODE it satisfies and showing it is regular singular at $\zeta=0$.

Roughly speaking, factoring out $e^{-\alpha_j z}$ removes the constant term of $P$, and factoring out $z^{-\tau_j}$ changes $Q$ to give factorial growth instead of gamma function growth (?).

\begin{align*}
\mathcal{P} & = \sum_j^d f_j \frac{\partial}{\partial z}^j \\
& = \sum_j^d f_j \left(-\frac{1}{w^2} \frac{\partial}{\partial w}\right)^j\\
&=  \sum_j^d \tilde{f}_j \frac{\partial}{\partial w}^j
\end{align*}
where $w=1/z$.  if $\tilde{f}_j $ has a pole of order at most $d-j$ at 0 then it's regular singular, otherwise it's irregular. The relevant term should be
\color{Tan}
\[ \left(\frac{P_d}{w^{2d}} + \frac{R_d(w)}{w^{2d-2}}\right) \left(\frac{\partial}{\partial w}\right)^d , \]
\color{DarkTurquoise}
\[ \frac{P_d}{w^{2d}}  \left(\frac{\partial}{\partial w}\right)^d , \]
corresponding to the quadratic differential $dw^2/w^{2d}$, whose trajectories form $2(d-1)$ half-planes around $\infty$ (see Bridgeland \& Smith's ``Quadratic differential as stability conditions,'' Figure~10).

From the Bessel equation, for example, we get
\begin{align*}
(-w^{-2}\partial_w)^2&=-w^{-2}\partial_w(-w^{-2}\partial_w)\\
&=-w^{-2}(2w^{-3}\partial_w-w^{-2}\partial_w^2)\\
&=-2w^{-5}\partial_w+w^{-4}\partial_w^2,
\end{align*}
giving two half-planes around $\infty$, as expected.
\color{black}

Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
\begin{equation}\label{formal solution}
\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
\end{equation}
where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$. Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.

Classically it has been proved that the formal solutions $\series{\Psi}_j$ in \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Braaksma,Loday-Richaud, check]}. Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method \textbf{(see Balser chap. 14)}. Conversely, we can explicitly build a distinguished basis of analytic solutions:

\begin{theorem}[see Theorem \ref{thm1-dim}]\label{thm1}
In the previous set-up, for every $\alpha_j$ we set $\zeta_j=\zeta-\alpha_j$. Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with

\begin{equation}
\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
\end{equation}

such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ for a small compact domain $\Omega\subset\C$. 
\end{theorem}

At this point, we may ask what is the relationship between the two frame of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$. Our main result says they are actually the same, hence proving Borel summation works.

\begin{theorem}\label{thm2}
For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
\end{theorem}

In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.

>>>>

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{tikz-cd}
% convenience aliases
\newcommand{\maps}{\colon}

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}

@@

\newtheorem{definition}{Definition}[section]
\newtheorem{prop}[definition]{Proposition}
\newtheorem{remark}[definition]{Remark}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[definition]{Lemma}
%\newtheorem{conjecture}[definition]{Conjecture}
\newtheorem{claim}[definition]{Claim}
%\newtheorem{exercise}[definition]{Exercise}
%\newtheorem*{notation*}{Notation}

% drafting environments
\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}

% colors
\definecolor{ietocean}{RGB}{0, 30, 140}
\definecolor{ietcoast}{RGB}{0, 150, 173}
\definecolor{ietlagoon}{RGB}{0, 216, 180}

% pretty prince hyperref must always be the last thing in the preamble, always
\usepackage{hyperref}
\hypersetup{
  colorlinks,
  linkcolor={ietcoast},
  citecolor={ietcoast},
  urlcolor={ietcoast}
}

\title{Higher Airy}
\author{Veronica Fantini}

@@
